Improving real-time trend estimates using local parametrisation of polynomial regression filters

### 2024-04-17 paper/article_jos.qmd
improvement

---
title: "Improving real-time trend estimates using local parametrisation of polynomial regression filters"
format:
  pdf:
    documentclass: article
    number-sections: true
    pdf-engine: pdflatex
    keep-tex: true
    toc: false
    include-in-header: [preamble.tex]
    #include-before-body: template/preambule.tex
    geometry:
      - top=2cm
      - bottom=2cm
      - left = 2.5cm
      - right = 2.5cm
    cite-method: biblatex
linestretch: 2
echo: false
tbl-cap-location: top
fig-cap-location: top
bibliography: biblio.bib
csl: chicago-author-date.csl
---

@@

A moving average, or linear filter, is a statistical method that consists of applying a rolling weighted mean to a times series: for each date $t$ it computes a weighted mean of $p$ past points and $q$ future points where $p,q\geq0$ depends on the moving average.
Moving averages are ubiquitous in business cycle extraction and seasonal adjustment methods.
For example, the X-13ARIMA seasonal adjustment method uses several moving averages to estimate the main components of a time series. 
Symmetric filters are applied to the center of the series, but when it comes to estimate the most recent points, all of these methods must rely on asymmetric filters. 
For trend-cycle extraction, the most popular symmetric filter is the @henderson1916note moving average, which is used in the X-13ARIMA seasonal adjustment algorithm.

However, for real-time estimates, due to the lack of future observations, all these methods must rely on asymmetric filters to estimate the most recent points. 
For example, for trend-cycle extraction, X-13ARIMA uses Henderson's symmetric filter and @musgrave1964set's asymmetric filters on an extended series using an ARIMA model.
Since the predicted values are linear combinations of past values, this amounts to applying asymmetric averages at the end of the series.

@@

Using local polynomial regression, @proietti2008 developed a general class of symmetric and asymmetric moving averages.
In particular, it becomes possible to reproduce Henderson's symmetric filter and Musgrave's asymmetric filters.
However, these methods have two drawbacks.
Firstly, the phase shift (i.e. the delay in detecting turning points) is not directly controlled.
Secondly, asymmetric filters depend on a parameter that is generally estimated over the whole series using assumptions that may be wrong locally.
The aim of this study is to propose extensions to the @proietti2008 class of filters in order to take these shortcomings into account.
The extensions have been implemented in the R `rjd3filters` package (available at <https://github.com/rjdemetra/rjd3filters>) and are therefore easily reusable.

@@

To interpret the notions of gain and phase shift, it is useful to illustrate the effects of moving averages on harmonic series $X_t=\e^{-i\omega t}$ with $\omega\in[0,\pi]$.
The moving average $M_{\boldsymbol\theta}$ transforms $X_t$ into:
$$
Y_t = M_{\boldsymbol\theta}X_t = \sum_{k=-p}^{+f} \theta_k \e^{-i \omega (t+k)}
= \left(\sum_{k=-p}^{+f} \theta_k \e^{-i \omega k}\right)\cdot X_t.
$$
The function  $\Gamma_{\boldsymbol\theta}(\omega)=\sum_{k=-p}^{+f} \theta_k e^{-i \omega k}$ is called the *transfer function* or *frequency response function*.
The frequency response function can alternatively be defined as $\Gamma_{\boldsymbol\theta}(\omega)=\sum_{k=-p}^{+f} \theta_k e^{i \omega k}$ or $\Gamma_{\boldsymbol\theta}(\omega)=\sum_{k=-p}^{+f} \theta_k e^{2\pi i \omega k}$.
It can be rewritten as:
$$
\Gamma_{\boldsymbol\theta}(\omega) = \rho_{\boldsymbol\theta}(\omega)\e^{i\varphi_{\boldsymbol\theta}(\omega)},
$$
where  $\rho_{\boldsymbol\theta}(\omega)=G_{\boldsymbol\theta}(\omega)=\lvert\Gamma_{\boldsymbol\theta}(\omega)\rvert$ is the *gain* or *amplitude* function and $\varphi_{\boldsymbol\theta}(\omega)$ is the *phase shift* or *time shift* function.
This function is sometimes represented as $\phi_{\boldsymbol\theta}(\omega)=\frac{\varphi_{\boldsymbol\theta}(\omega)}{\omega}$ to measure the phase shift in number of periods.
For all symmetric moving averages we have $\varphi_{\boldsymbol\theta}(\omega)\equiv 0 \;(modulo\;{\pi})$.

@@

To decompose a time series into a seasonal component, a trend-cycle and the irregular, the X-11 decomposition algorithm (used in X-13ARIMA) uses a succession of moving averages, all with specific constraints.

@@

- $M_{\boldsymbol\theta}$ preserves polynomials of degree $d$ if and only if:
$$
\sum_{k=-p}^{+f}\theta_k=1
 \text{ and }
\forall j \in \left\llbracket 1,d\right\rrbracket:\:
\sum_{k=-p}^{+f}k^j\theta_k=0.
$$
- If $M_{\boldsymbol\theta}$ is symmetric ($p=f$ and $\theta_{-k} = \theta_k$) and preserves polynomials of degree $2d$ then it also preserves polynomials of degree $2d+1$.

@@

2. Apply symmetric filters to extended forecast series.
This method seems to date back to @deforest1877adjustment, which also suggests modelling a polynomial trend of degree three or less at the end of the period.
A similar approach is used in the X-13ARIMA seasonal adjustment method: the series is extend by one year (by default) with an ARIMA model to minimise the revisions associated to asymmetric filters

@@

Conversely, the implicit forecasts of an asymmetric moving average can be deduced from a reference symmetric moving average. 
This allows us to judge the quality of real-time estimates of the trend-cycle and to anticipate future revisions when forecasts are far from expected evolutions.\
Let us denote $v=(v_{-h},\dots, v_{h})$ the reference symmetric moving average and $w^0,\dots w^{h-1}$ a sequence of asymmetric moving averages, of order $h+1$ to $2h$ used to estimate the last $h$ points with, for convention, $w_t^q=0$ for $t>q$.
This means that $w^0=(w_{-h}^0,\dots, w_{0}^0)$ is used for estimation in real time (when no points are known in the future), $w^1=(w_{-h}^1,\dots, w_{1}^1)$ for estimation of the penultimate point (when only one point is known in the future), and so on.
Let also note $y_{-h},\dots,y_{0}$ the observed series studied and $y_{1}^*,\dots y_h^*$ the implicit forecast induced by $w^0,\dots w^{h-1}$.
This means that for all $q$ we have:
$$
\underbrace{\sum_{i=-h}^0 v_iy_i + \sum_{i=1}^h v_iy_i^*}_{\text{smoothing by }v\text{ of the extended series}}
=\underbrace{\sum_{i=-h}^0 w_i^qy_i + \sum_{i=1}^h w_i^qy_i^*}_{\text{smoothing by }w^q\text{ of the extended series}}.
$$
This is equivalent to:
$$
\quad \sum_{i=1}^h (v_i- w_i^q) y_i^*
=\sum_{i=-h}^0 (w_i^q-v_i)y_i.
$$
To sum up, in matrix form, this is equivalent to solving:
$$
\scriptstyle
\begin{pmatrix}
  v_1 & v_2 & \cdots & v_h \\
  v_1 - w_1^1 & v_2 & \cdots & v_h \\
  \vdots & \vdots & \cdots & \vdots \\
   v_1 - w_1^{h-1} & v_2-w_2^{h-1} & \cdots & v_h
\end{pmatrix}
\begin{pmatrix}y_1^* \\ \vdots \\ y_h^*\end{pmatrix}=
\begin{pmatrix}
  w_{-h}^0 - v_{-h} & w_{-(h-1)}^0 - v_{-(h-1)} & \cdots & w_{0}^0 - v_{0} \\
  w_{-h}^1 - v_{-h} & w_{-(h-1)}^1 - v_{-(h-1)} & \cdots & w_{0}^1 - v_{0} \\
  \vdots & \vdots & \cdots & \vdots \\
  w_{-h}^{h-1} - v_{-h} & w_{-(h-1)}^{h-1} - v_{-(h-1)} & \cdots & w_{0}^{h-1} - v_{0}
\end{pmatrix}
\begin{pmatrix}y_{-h} \\ \vdots \\ y_0\end{pmatrix}.
$$
This is implemented in the `rjd3filters::implicit_forecast()` function.

@@

Using @proietti2008's notation, we assume that our time series $y_t$ can be decomposed into
$$
y_t=\mu_t+\varepsilon_t,
$$
where $\mu_t$ is the trend and $\varepsilon_{t}\overset{i.i.d}{\sim}\mathcal{N}(0,\sigma^{2})$ is the noise (the series is therefore seasonally adjusted).
Within a neighbourhood $h$ of $t$, the local trend $\mu_t$ is approximated by a polynomial of degree $d$, such that $\mu_t\simeq m_{t}$ with:
$$
\forall j\in\left\llbracket -h,h\right\rrbracket:\:
y_{t+j}=m_{t+j}+\varepsilon_{t+j},\quad m_{t+j}=\sum_{i=0}^{d}\beta_{i}j^{i}.
$$
The problem of trend extraction is equivalent to estimating $m_t=\beta_0$ (the constant in the previous formula).

In matrix notation:
$$
\underbrace{\begin{pmatrix}y_{t-h}\\
y_{t-(h-1)}\\
\vdots\\
y_{t}\\
\vdots\\
y_{t+(h-1)}\\
y_{t+h}
\end{pmatrix}}_{\boldsymbol y}=\underbrace{\begin{pmatrix}1 & -h & h^{2} & \cdots & (-h)^{d}\\
1 & -(h-1) & (h-1)^{2} & \cdots & (-(h-1))^{d}\\
\vdots & \vdots & \vdots & \cdots & \vdots\\
1 & 0 & 0 & \cdots & 0\\
\vdots & \vdots & \vdots & \cdots & \vdots\\
1 & h-1 & (h-1)^{2} & \cdots & (h-1)^{d}\\
1 & h & h^{2} & \cdots & h^{d}
\end{pmatrix}}_{\boldsymbol X}\underbrace{\begin{pmatrix}\beta_{0}\\
\beta_{1}\\
\vdots\\
\vdots\\
\vdots\\
\vdots\\
\beta_{d}
\end{pmatrix}}_{\boldsymbol \beta}+\underbrace{\begin{pmatrix}\varepsilon_{t-h}\\
\varepsilon_{t-(h-1)}\\
\vdots\\
\varepsilon_{t}\\
\vdots\\
\varepsilon_{t+(h-1)}\\
\varepsilon_{t+h}
\end{pmatrix}}_{\boldsymbol \varepsilon}.
$$

To estimate $\boldsymbol \beta$ we need at least $d+1$ observations (thus $2h\geq d$) and the estimation is made by weighted least squares (WLS), which is equivalent to minimising the following objective function:
$$
S(\hat{\beta}_{0},\dots,\hat{\beta}_{d})=\sum_{j=-h}^{h}\kappa_{j}(y_{t+j}-\hat{\beta}_{0}-\hat{\beta}_{1}j-\dots-\hat{\beta}_{d}j^{d})^{2}.
$$
where $\kappa_j$ is a set of weights called a *kernel*.
We have $\kappa_j\geq 0:\kappa_{-j}=\kappa_j$, and with $\boldsymbol K=diag(\kappa_{-h},\dots,\kappa_{h})$, the estimate of $\boldsymbol \beta$ can be written as $\hat{\boldsymbol\beta}=(\boldsymbol X'\boldsymbol K\boldsymbol X)^{-1}\boldsymbol X'\boldsymbol K\boldsymbol y.$
With $\boldsymbol e_1=\transp{\begin{pmatrix}1 &0 &\cdots&0 \end{pmatrix}}$, the estimate of the trend is:
$$
\hat{m}_{t}=\boldsymbol e_{1}\hat{\boldsymbol \beta}=\boldsymbol \theta'\boldsymbol y=\sum_{j=-h}^{h}\theta_{j}y_{t-j}\text{ with }\boldsymbol \theta=\boldsymbol K\boldsymbol X(\boldsymbol X'\boldsymbol K\boldsymbol X)^{-1}\boldsymbol e_{1}.
$$ {#eq-mmsym}
To conclude, the estimate of the trend $\hat{m}_{t}$ can be obtained applying the symmetric filter $\boldsymbol \theta$ to $y_t$ ($\boldsymbol \theta$ is symmetric due to the symmetry of the kernel weights $\kappa_j$).
Moreover, $\boldsymbol X'\boldsymbol \theta=\boldsymbol e_{1}$ so:
$$
\sum_{j=-h}^{h}\theta_{j}=1,\quad\forall r\in\left\llbracket 1,d\right\rrbracket:\sum_{j=-h}^{h}j^{r}\theta_{j}=0.
$$
Hence, the filter $\boldsymbol w$ preserves deterministic polynomials of order $d$.

@@

1. Apply symmetric filters to the series extended by forecasting $\hat{y}_{n+l\mid n},l\in\left\llbracket 1,h\right\rrbracket$.

2. Build an asymmetric filter by local polynomial approximation on the available observations ($y_{t}$ for $t\in\left\llbracket n-h,n\right\rrbracket$).

@@

To solve the problem of the variance of real-time filter estimates, @proietti2008 propose a general method for constructing asymmetric filters that allows a bias-variance trade-off.
This is a generalisation of @musgrave1964set's asymmetric filters (used in the X-13ARIMA seasonal adjustment algorithm).

The initial series is modelled here as:
$$
\boldsymbol y=\boldsymbol U \boldsymbol \gamma+\boldsymbol Z\boldsymbol \delta+\boldsymbol \varepsilon,\quad
\boldsymbol \varepsilon\sim\mathcal{N}(0,\boldsymbol D).
$$ {#eq-lpgeneralmodel}
where $[\boldsymbol U,\boldsymbol Z]$ is of full rank and forms a subset of the columns of $X$.
The objective is to find a filter $\boldsymbol v$ that minimises the mean square error of revision (to the symmetric filter $\boldsymbol \theta$) under certain constraints.
These constraints are represented by the matrix $\boldsymbol U=\transp{\begin{pmatrix} \transp{\boldsymbol U_{p}}& \transp{\boldsymbol U_{f}}\end{pmatrix}}$: $\boldsymbol U_p'\boldsymbol v=\boldsymbol U'\boldsymbol \theta$ (with $\boldsymbol U_p$ the $(h+q+1)\times (d+1)$ matrix which contains the observations of the matrix $U$ known during estimation by the asymmetric filter).
The problem is equivalent to finding $v$ which minimises:
$$
\varphi(\boldsymbol v)=
\underbrace{
  \underbrace{(\boldsymbol v-\boldsymbol \theta_{p})'\boldsymbol D_{p}(\boldsymbol v-\boldsymbol \theta_{p})+
  \boldsymbol \theta_{f}'\boldsymbol D_{f}\boldsymbol \theta_{f}}_\text{revision error variance}+
  \underbrace{[\boldsymbol \delta'(\boldsymbol Z_{p}'\boldsymbol v-\boldsymbol Z'\boldsymbol \theta)]^{2}}_{bias^2}
}_\text{mean square revision error}+
\underbrace{2\boldsymbol l'(\boldsymbol U_{p}'\boldsymbol v-\boldsymbol U'\boldsymbol \theta)}_{\text{constraints}}.
$$ {#eq-lppasym}
where $\boldsymbol l$ is a vector of Lagrange multipliers.

@@

When $\boldsymbol U=\transp{\begin{pmatrix}1&\cdots&1\end{pmatrix}}$, $\boldsymbol Z=\transp{\begin{pmatrix}-h&\cdots&+h\end{pmatrix}}$, $\boldsymbol \delta=\delta_1$, $\boldsymbol D=\sigma^2\boldsymbol I$ and when the symmetric filter is the Henderson filter, we find the asymmetric Musgrave filters (using the Henderson kernel).
This filter assumes that, for real-time estimation, the data is generated by a linear process and that the asymmetric filters preserve the constants ($\sum v_i=\sum \theta_i=1$).
These asymmetric filters depend on the ratio $\lvert\delta_1/\sigma\rvert$, which, assuming that the trend is linear and the bias constant, can be linked to the I-C ratio $R=\frac{\bar{I}}{\bar{C}}=\frac{\sum\lvert I_t-I_{t-1}\rvert}{\sum\lvert C_t-C_{t-1}\rvert}$: $\delta_1/\sigma=2/(R\sqrt{\pi})$.
This ratio is used in particular in X-13ARIMA to determine the length of the Henderson filter. 
For monthly data:

@@

```{r, echo=FALSE, out.width="100%", fig.note = footnotes}
#| label: fig-graphstpsimul
#| fig-cap: Distribution of phase shifts on simulated series.
img <- sprintf("img/simulations/phase_shift_simul.%s", "pdf")
knitr::include_graphics(img)
```

>>>>

---
title: "Improving real-time trend estimates using local parametrisation of polynomial regression filters"
format:
  pdf:
    documentclass: article
    number-sections: true
    pdf-engine: pdflatex
    keep-tex: true
    toc: false
    include-in-header: [preamble.tex]
    #include-before-body: template/preambule.tex
    geometry:
      - top=2cm
      - bottom=2cm
      - left = 2.5cm
      - right = 2.5cm
    cite-method: biblatex
crossref:
  tbl-prefix: table
  fig-prefix: figure
  sec-prefix: section
linestretch: 2
echo: false
tbl-cap-location: top
fig-cap-location: top
bibliography: biblio.bib
csl: chicago-author-date.csl
---

@@

A moving average, or linear filter, is a statistical method that consists of applying a rolling weighted mean to a times series: for each date $t$ it computes a weighted mean of $p$ past points and $q$ future points where $p,q\geq0$ depends on the moving average.
Moving averages are ubiquitous in business cycle extraction and seasonal adjustment methods.
For example, the X-11 decomposition method (used in X-13ARIMA-SEATS) uses several moving averages to estimate the main components of a time series. 
Symmetric filters are applied to the center of the series, but when it comes to estimate the most recent points, all of these methods must rely on asymmetric filters. 
For trend-cycle extraction, the most popular symmetric filter is the @henderson1916note moving average, which is used in the X-11 seasonal adjustment algorithm.

However, for real-time estimates, due to the lack of future observations, all these methods must rely on asymmetric filters to estimate the most recent points. 
For example, for trend-cycle extraction, X-11 uses Henderson's symmetric filter and @musgrave1964set's asymmetric filters on an extended series using an ARIMA model.
Since the predicted values are linear combinations of past values, this amounts to applying asymmetric averages at the end of the series.

@@

Using local polynomial regression, @proietti2008 developed a general class of symmetric and asymmetric moving averages.
In particular, it becomes possible to reproduce Henderson's symmetric filter and Musgrave's asymmetric filters.
However, these methods have two drawbacks.
Firstly, the phase shift (i.e. the delay in detecting turning points) is not directly controlled.
Secondly, asymmetric filters depend on a parameter that is generally estimated over the whole series using assumptions that may be wrong locally.
The aim of this study is to propose extensions to the @proietti2008 class of filters in order to take these shortcomings into account.
The extensions have been implemented in the R `rjd3filters` package (available at <https://github.com/rjdemetra/rjd3filters>) and can therefore be easily used.

@@

To interpret the notions of gain and phase shift, it is useful to illustrate the effects of moving averages on harmonic series $X_t=\e^{-i\omega t}$ with $\omega\in[0,\pi]$.
The moving average $M_{\boldsymbol\theta}$ transforms $X_t$ into:
$$
Y_t = M_{\boldsymbol\theta}X_t = \sum_{k=-p}^{+f} \theta_k \e^{-i \omega (t+k)}
= \left(\sum_{k=-p}^{+f} \theta_k \e^{-i \omega k}\right)\cdot X_t.
$$
The function  $\Gamma_{\boldsymbol\theta}(\omega)=\sum_{k=-p}^{+f} \theta_k e^{-i \omega k}$ is called the *transfer function* or *frequency response function*.
The frequency response function can alternatively be defined as $\Gamma_{\boldsymbol\theta}(\omega)=\sum_{k=-p}^{+f} \theta_k e^{i \omega k}$ or $\Gamma_{\boldsymbol\theta}(\omega)=\sum_{k=-p}^{+f} \theta_k e^{2\pi i \omega k}$.
It can be rewritten as:
$$
\Gamma_{\boldsymbol\theta}(\omega) = \rho_{\boldsymbol\theta}(\omega)\e^{i\varphi_{\boldsymbol\theta}(\omega)},
$$
where  $\rho_{\boldsymbol\theta}(\omega)=G_{\boldsymbol\theta}(\omega)=\lvert\Gamma_{\boldsymbol\theta}(\omega)\rvert$ is the *gain* or *amplitude* function and $\varphi_{\boldsymbol\theta}(\omega)$ is the *phase shift* or *time shift* function.
We this have:
\begin{align*}
\rho_{\boldsymbol\theta}(\omega) &=\sqrt{\left(\sum_{k=-p}^{+f}\theta_k\cos(\omega k)\right)^2+
\left(\sum_{k=-p}^{+f}\theta_k\sin(\omega k)\right)^2} \\
\tan \varphi_{\boldsymbol\theta}(\omega) &=- \frac{\sum_{k=-p}^{+f}\theta_k\sin(\omega k)}{\sum_{k=-p}^{+f}\theta_k\cos(\omega k)} \text{ if }\sum_{k=-p}^{+f}\theta_k\cos(\omega k) \ne 0 \\
&= 0 \text{ if }\sum_{k=-p}^{+f}\theta_k\cos(\omega k) = 0.
\end{align*}
The phase shift is sometimes represented as $\phi_{\boldsymbol\theta}(\omega)=\frac{\varphi_{\boldsymbol\theta}(\omega)}{\omega}$ to measure it in number of periods.
For all symmetric moving averages we have $\varphi_{\boldsymbol\theta}(\omega)\equiv 0 \;(modulo\;{\pi})$.

@@

To decompose a time series into a seasonal component, a trend-cycle and the irregular, the X-11 decomposition algorithm (used in X-13ARIMA-SEATS) uses a succession of moving averages, all with specific constraints.

@@

- $M_{\boldsymbol\theta}$ preserves polynomials of degree $d$ if and only if:
$$
\sum_{k=-p}^{+f}\theta_k=1
 \text{ and }
\forall j \in \left\{1,2,\dots,d\right\}:\:
\sum_{k=-p}^{+f}k^j\theta_k=0.
$$
- If $M_{\boldsymbol\theta}$ is symmetric ($p=f$ and $\theta_{-k} = \theta_k$) and preserves polynomials of degree $2d$ then it also preserves polynomials of degree $2d+1$.

@@

2. Apply symmetric filters to extended forecast series.
This method seems to date back to @deforest1877adjustment, which also suggests modelling a polynomial trend of degree three or less at the end of the period.
A similar approach is used in the X-13ARIMA-SEATS seasonal adjustment method: the series is extend by one year (by default) with an ARIMA model to minimise the revisions associated to asymmetric filters

@@

Conversely, the implicit forecasts of an asymmetric moving average can be deduced from a reference symmetric moving average. 
This allows us to judge the quality of real-time estimates of the trend-cycle and to anticipate future revisions when forecasts are far from expected evolutions.\
Let us denote $\boldsymbol v=(v_{-h},\dots, v_{h})$ the reference symmetric moving average (used to compute the final estimates) and $\boldsymbol w^0,\dots, \boldsymbol w^{h-1}$ a sequence of asymmetric moving averages used for the intermediate estimates. 
$\boldsymbol w^0=(w_{-h}^0, \dots, w_{0}^0)$ is used for estimation in real time estimate (when 0 point in the future is known), $\boldsymbol w^1=(w_{-h}^1, \dots, w_{0}^1, w_{1}^1)$ is used for estimation of the penultimate point (when only 1 in the future is known), and so on.
Let $y_{t-h},\dots,y_{t}$ be the observed series during the last $h$ periods (for which asymmetric moving averages are used to get the intermediate trend-cycle estimates for the dates $t-h$ to $h$). 
The implicit forecast $y_{t+1}^*,\dots y_{t+h}^*$ induced by $w^0,\dots w^{h-1}$ are the forecasts of the series $y_t$ for which the estimates of the symmetric filter applied to the extended series $\boldsymbol y^* = (y_{t-h}, \dots, y_t, y_{t+1}^*,\dots y_{t+h}^*)$ produce the same estimates as the asymmetric filter applied to the series $\boldsymbol y^*$.
This means:
\begin{align*}
\underbrace{\sum_{i=-h}^0 v_iy_{ti} + \sum_{i=1}^h v_iy_{t+i}^*}_{\text{smoothing by }\boldsymbol v\text{ of the extended series}} &=
\underbrace{\sum_{i=-h}^0 w_i^0y_{t+i}}_{\text{smoothing by }\boldsymbol w^0\text{ using }0\text{ points after }t} \\
&=
\underbrace{\sum_{i=-h}^0 w_i^1y_{t+i} + w_1^1y_{t+1}^*}_{\text{smoothing by }\boldsymbol w^1\text{ using }1\text{ points after }t} \\
&= \underbrace{\sum_{i=-h}^0 w_i^2y_{t+i} + \sum_{i=1}{2}w_i^2y_{t+i}^*}_{\text{smoothing by }\boldsymbol w^2\text{ using }2\text{ points after }t} \\
&= \cdots \\
&=\underbrace{\sum_{i=-h}^0 w_i^{h-1}y_{t+i} + \sum_{i=1}^{h-1} w_i^{h-1}y_{t+i}^*}_{\text{smoothing by }\boldsymbol w^{h-1}\text{ using }h-1\text{ points after }t}
\end{align*}
For any integer $q$ between 0 and $h-1$, using for convention $w_t^q=0$ if $t>q$ we then have:
$$
\sum_{i=1}^h (v_i- w_i^q) y_i^*
=\sum_{i=-h}^0 (w_i^q-v_i)y_i.
$$
In matrix form, this is equivalent to solving:
$$
\scriptstyle
\begin{pmatrix}
  v_1 & v_2 & \cdots & v_h \\
  v_1 - w_1^1 & v_2 & \cdots & v_h \\
  \vdots & \vdots & \cdots & \vdots \\
   v_1 - w_1^{h-1} & v_2-w_2^{h-1} & \cdots & v_h
\end{pmatrix}
\begin{pmatrix}y_1^* \\ \vdots \\ y_h^*\end{pmatrix}=
\begin{pmatrix}
  w_{-h}^0 - v_{-h} & w_{-(h-1)}^0 - v_{-(h-1)} & \cdots & w_{0}^0 - v_{0} \\
  w_{-h}^1 - v_{-h} & w_{-(h-1)}^1 - v_{-(h-1)} & \cdots & w_{0}^1 - v_{0} \\
  \vdots & \vdots & \cdots & \vdots \\
  w_{-h}^{h-1} - v_{-h} & w_{-(h-1)}^{h-1} - v_{-(h-1)} & \cdots & w_{0}^{h-1} - v_{0}
\end{pmatrix}
\begin{pmatrix}y_{-h} \\ \vdots \\ y_0\end{pmatrix}.
$$
This is implemented in the `rjd3filters::implicit_forecast()` function.

@@

Using @proietti2008's notation, we assume that our time series $y_t$ can be decomposed into
$$
y_t=\mu_t+\varepsilon_t,
$$
where $\mu_t$ is the trend and $\varepsilon_{t}\overset{i.i.d}{\sim}\mathcal{N}(0,\sigma^{2})$ is the noise (the series is therefore seasonally adjusted).
Within a neighbourhood $h$ of $t$, the local trend $\mu_t$ is approximated by a polynomial of degree $d$, such that $\mu_t\simeq m_{t}$ with:
$$
\forall j\in\left\{-h,-h+1,\dots,h\right\}:\:
y_{t+j}=m_{t+j}+\varepsilon_{t+j},\quad m_{t+j}=\sum_{i=0}^{d}\beta_{i}j^{i}.
$$
The problem of trend extraction is equivalent to estimating $m_t=\beta_0$ (the constant in the previous formula).

In matrix notation:
$$
\underbrace{\begin{pmatrix}y_{t-h}\\
y_{t-(h-1)}\\
\vdots\\
y_{t}\\
\vdots\\
y_{t+(h-1)}\\
y_{t+h}
\end{pmatrix}}_{\boldsymbol y}=\underbrace{\begin{pmatrix}1 & -h & h^{2} & \cdots & (-h)^{d}\\
1 & -(h-1) & (h-1)^{2} & \cdots & (-(h-1))^{d}\\
\vdots & \vdots & \vdots & \cdots & \vdots\\
1 & 0 & 0 & \cdots & 0\\
\vdots & \vdots & \vdots & \cdots & \vdots\\
1 & h-1 & (h-1)^{2} & \cdots & (h-1)^{d}\\
1 & h & h^{2} & \cdots & h^{d}
\end{pmatrix}}_{\boldsymbol X}\underbrace{\begin{pmatrix}\beta_{0}\\
\beta_{1}\\
\vdots\\
\vdots\\
\vdots\\
\vdots\\
\beta_{d}
\end{pmatrix}}_{\boldsymbol \beta}+\underbrace{\begin{pmatrix}\varepsilon_{t-h}\\
\varepsilon_{t-(h-1)}\\
\vdots\\
\varepsilon_{t}\\
\vdots\\
\varepsilon_{t+(h-1)}\\
\varepsilon_{t+h}
\end{pmatrix}}_{\boldsymbol \varepsilon}.
$$ {#eq-lpp}

Since $d+1$ parameters are estimated with $\boldsymbol \beta$, we need at least $2h+1$ observations (thus $2h\geq d$) and the estimation is made by weighted least squares (WLS), which is equivalent to minimising the following objective function:
$$
S(\hat{\beta}_{0},\dots,\hat{\beta}_{d})=\sum_{j=-h}^{h}\kappa_{j}(y_{t+j}-\hat{\beta}_{0}-\hat{\beta}_{1}j-\dots-\hat{\beta}_{d}j^{d})^{2}.
$$
where $\kappa_j$ is a set of weights called a *kernel*.
We have $\kappa_j\geq 0:\kappa_{-j}=\kappa_j$, and with $\boldsymbol K=diag(\kappa_{-h},\dots,\kappa_{h})$, the estimate of $\boldsymbol \beta$ can be written as $\hat{\boldsymbol\beta}=(\transp{\boldsymbol X}\boldsymbol K\boldsymbol X)^{-1}\transp{\boldsymbol X}\boldsymbol K\boldsymbol y.$
With $\boldsymbol e_1=\transp{\begin{pmatrix}1 &0 &\cdots&0 \end{pmatrix}}$, the estimate of the trend is:
$$
\hat{m}_{t}=\boldsymbol e_{1}\hat{\boldsymbol \beta}=\transp{\boldsymbol \theta}\boldsymbol y=\sum_{j=-h}^{h}\theta_{j}y_{t-j}\text{ with }\boldsymbol \theta=\boldsymbol K\boldsymbol X(\transp{\boldsymbol X}\boldsymbol K\boldsymbol X)^{-1}\boldsymbol e_{1}.
$$ {#eq-mmsym}
To conclude, the estimate of the trend $\hat{m}_{t}$ can be obtained applying the symmetric filter $\boldsymbol \theta$ to $y_t$ ($\boldsymbol \theta$ is symmetric due to the symmetry of the kernel weights $\kappa_j$).
Moreover, since $\transp{\boldsymbol X}\boldsymbol \theta=\boldsymbol e_{1}$ we have:
$$
\sum_{j=-h}^{h}\theta_{j}=1,\quad\forall r\in\left\{1,2,\dots,d\right\}:\sum_{j=-h}^{h}j^{r}\theta_{j}=0.
$$
Hence, the filter $\boldsymbol w$ preserves deterministic polynomials of order $d$.

@@

1. Apply symmetric filters to the series extended by forecasting $\hat{y}_{n+l\mid n},l\in\left\{1,2,\dots,h\right\}$.

2. Build an asymmetric filter by local polynomial approximation on the available observations ($y_{t}$ for $t\in\left\{n-h,n-h+1,\dots,n\right\}$).

@@

To solve the problem of the variance of real-time filter estimates, @proietti2008 propose a general method for constructing asymmetric filters that allows a bias-variance trade-off.
This is a generalisation of @musgrave1964set's asymmetric filters (used in the X-11 seasonal adjustment algorithm).

Rewriting @eq-lpp:
$$
\boldsymbol y=\begin{pmatrix}\boldsymbol U &\boldsymbol Z\end{pmatrix}
\begin{pmatrix}\boldsymbol \gamma \\ \boldsymbol \delta\end{pmatrix}+\boldsymbol \varepsilon,\quad
\boldsymbol \varepsilon\sim\mathcal{N}(0,\boldsymbol D).
$$ {#eq-lpgeneralmodel}
where $[\boldsymbol U,\boldsymbol Z]$ is of full rank and forms a subset of the columns of $X$ and the variance of the error is defined as $\boldsymbol D = \sigma^2\boldsymbol K^{-1}$ to directly take into account the weights associated to the observations.
The objective is to find a filter $\boldsymbol v$ that minimises the mean square error of revision (to the symmetric filter $\boldsymbol \theta$) under certain constraints.
These constraints are represented by the matrix $\boldsymbol U=\transp{\begin{pmatrix} \transp{\boldsymbol U_{p}}& \transp{\boldsymbol U_{f}}\end{pmatrix}}$: $\transp{\boldsymbol U_p}\boldsymbol v=\transp{\boldsymbol U}\boldsymbol \theta$ (with $\boldsymbol U_p$ the $(h+q+1)\times (d+1)$ matrix which contains the observations of the matrix $U$ known during estimation by the asymmetric filter).
The problem is equivalent to finding $v$ which minimises:
$$
\varphi(\boldsymbol v)=
\underbrace{
  \underbrace{\transp{(\boldsymbol v-\boldsymbol \theta_{p})}\boldsymbol D_{p}(\boldsymbol v-\boldsymbol \theta_{p})+
  \transp{\boldsymbol \theta_{f}}\boldsymbol D_{f}\boldsymbol \theta_{f}}_\text{revision error variance}+
  \underbrace{[\transp{\boldsymbol \delta}(\transp{\boldsymbol Z_{p}}\boldsymbol v-\transp{\boldsymbol Z}\boldsymbol \theta)]^{2}}_{bias^2}
}_\text{mean square revision error}+
\underbrace{2\transp{\boldsymbol l}(\transp{\boldsymbol U_{p}}\boldsymbol v-\transp{\boldsymbol U}\boldsymbol \theta)}_{\text{constraints}}.
$$ {#eq-lppasym}
where $\boldsymbol l$ is a vector of Lagrange multipliers.

@@

When $\boldsymbol U=\transp{\begin{pmatrix}1&\cdots&1\end{pmatrix}}$, $\boldsymbol Z=\transp{\begin{pmatrix}-h&\cdots&+h\end{pmatrix}}$, $\boldsymbol \delta=\delta_1$, $\boldsymbol D=\sigma^2\boldsymbol I$ and when the symmetric filter is the Henderson filter, we find the asymmetric Musgrave filters (using the Henderson kernel).
This filter assumes that, for real-time estimation, the data is generated by a linear process and that the asymmetric filters preserve the constants ($\sum v_i=\sum \theta_i=1$).
These asymmetric filters depend on the ratio $\lvert\delta_1/\sigma\rvert$, which, assuming that the trend is linear and the bias constant, can be linked to the I-C ratio $R=\frac{\bar{I}}{\bar{C}}=\frac{\sum\lvert I_t-I_{t-1}\rvert}{\sum\lvert C_t-C_{t-1}\rvert}$: $\delta_1/\sigma=2/(R\sqrt{\pi})$.
This ratio is used in particular in X-11 to determine the length of the Henderson filter. 
For monthly data:

@@

```{r, echo=FALSE, out.width="100%"}
#| label: fig-graphstpsimul
#| fig-cap: Distribution of phase shifts on simulated series.
img <- sprintf("img/simulations/phase_shift_simul.%s", "pdf")
knitr::include_graphics(img)
```
